---
title: "Introduction to nppesapi"
author: "Brandon Greenwell and Dan Garmat"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to nppesapi}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
---

```{r setup, echo = FALSE}
knitr::opts_chunk$set(echo = TRUE, fig.width = 5, fig.height = 5)
```

The `nppesapi` package queries the NPPES API with an R wrapper. It allows systems to access NPPES public data in real-time, rather than through batched uploads. The API retrieves data from NPPES daily. 


For example, suppose we want to look up Dayton Children's Orthopedic Center for Spinal & Pediatric Care and know its NPI number 1124021324. We could query NPPES with:

```{r intro}
library(nppesapi)
nppes_api("number=1124021324")
```

You can perform more advanced queries of the NPPES API. A full list of accepting API code is [on the NPPES wesite](https://npiregistry.cms.hhs.gov/registry/help-api).

For instance, first 5 acupuncturists in zip code 97209:

```{r advanced}
query1 <- nppes_api("postal_code=97209&taxonomy_description=ACUPUNCTURIST&limit=5")
query1
```

If then want to extract some information, such as all NPIs, could do the following:
```{r advanced2}
acuvec <- unlist(lapply(query1$content$results, '[[', "number")) # get the NPI number
acuvec

```

Could also query a list of NPIs and use a custom function to extract a different field, such as ZIP. Here, using the same list, should all get 97209, and indeed do for primary practice address, addresses[[1]]:

```{r advanced3}
query2 <- (paste0("number=",acuvec))
names(query2) <- acuvec

npi_to_zip <- function(npi){
  nppes_result <- nppes_api(npi)
  zip <- nppes_result$content$results[[1]]$addresses[[1]]$postal_code
  zip <- substr(zip, 1, 5)
}

npilist <- lapply(query2, npi_to_zip)

table(unlist(npilist))  # hope to see 5 !!

```

