---
title: "Introduction to nppesapi"
author: "Brandon Greenwell and Dan Garmat"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to nppesapi}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
---

```{r setup, echo = FALSE}
knitr::opts_chunk$set(echo = TRUE, fig.width = 5, fig.height = 5)
```

The `nppesapi` package queries the NPPES API with an R wrapper. It allows systems to access NPPES public data in real-time, rather than through batched uploads. The API retrieves data from NPPES daily. 


For example, suppose we have a city we need to get information on all providers in Dayton. We could query NPPES with:

```{r intro}
library(nppesapi)
nppes_api("number=1124021324")
```

You can perform more advanced queries of the NPPES API. A full list of API codes is [on the NPPES wesite](https://npiregistry.cms.hhs.gov/registry/help-api).

For instance, Acupuncturists in zip code 97209:

```{r advanced}
query1 <- nppes_api("postal_code=97209&taxonomy_description=ACUPUNCTURIST")
query1
```

If then want to extract some information, such as all NPIs could do the following:
```{r advanced2}
acuvec <- unlist(lapply(query1$content$results, '[[', "number")) # get the NPI number
acuvec

```

Could also query a list of NPIs and extract a different field, such as ZIP. Here, using the same list, should all get 97209, but don't weirdly enough. The two office issue? Wrong field?:

```{r advanced3}
npilist <- lapply(paste0("number=",acuvec), nppes_api)
npilist

npilist2 <- (lapply(npilist, '[[', "content")) # there is an easier way to do this but I forgot it. Maybe with jsonlite?
npilist3 <- lapply(npilist2, '[[', "results")
for(i in 1:10){
  print(npilist3[[i]][[1]]$addresses[[2]]$postal_code)
}

```
