---
title: "Introduction to nppesapi"
author: "Brandon Greenwell, and Dan Garmat"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to nppesapi}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
---

```{r setup, echo = FALSE}
knitr::opts_chunk$set(echo = TRUE, fig.width = 5, fig.height = 5)
```

The `nppesapi` package queries the NPPES API with an R wrapper. It allows systems to access NPPES public data in real-time, rather than through batched uploads. The API retrieves data from NPPES daily. 


For example, suppose we have a city we need to get information on all providers in Dayton. We could query NPPES with:

```{r intro}
library(nppesapi)
nppes_api("city=dayton"))
```

You can perform more advanced queries of the NPPES API. A full list of API codes is [on the NPPES wesite](https://npiregistry.cms.hhs.gov/registry/help-api). 

For instance, all Acupuncturists in zip code 97209:

```{r advanced}
query1 <- nppes_api("postal_code=97209&taxonomy_description=ACUPUNCTURIST"))
query1
```

If then want to extract some information, such as all NPIs could do the following:
```{r advanced2}

```

Could also query a list of NPIs and extract a different field, such as ZIP. Here, using the same list, should all get 97209:

```{r advanced3}

```
